Enter our title here

### 2017-08-14 manuscript.tex
Update manuscript.tex

With this increased use of R in classrooms, there is a need for a more effective way to get students familiar with R. While R
software provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate this transition,
popular interactive teaching technologies have been created including Swirl (need to cite this?), LearnR and TryR. These tools 
allow students to work through coding problems while recieving immediate feedback in and out of the classroom. Swirl is an open source R software package 
that users access in their R console. This interactive learning tool contains several pre-existing lessons but what makes 
Swirl so popular is its versitality; educators can create their own lesson (or tailor a pre-existing one) to fit their 
curriculum and assign it to students \citep{Carchedi2014}.

@@

DataCamp is also a web application that offers interactive R programing courses but unlike TryR, educators can 
create their own courses that coincide with the lessons or assign a pre-existing DataCamp course. The DataCamp website offers 
free community courses as well as more specialized classes that you need to purchase. ... (i'll come back to this)

For a statistical learning tool to be effective, the software system should be modular, extensible, reproducable, and web-
based (Hare2017).

Modulariy is critical component in designing a statistical learning tool; it allows independent pieces to be easily added, 
modified or removed from the entire functionality (Hare2017).

\section{How to Use DataCamp}
Pre-existing courses:
DataCamp has a range of available free community courses that educators can utilize for supplimental R practice.

Creating a DataCamp Course:
To create a course on DataCamp you will first need to create a DataCamp account by visiting website\www.datacamp.com/teach and
have a GitHub account. The simplest way to begin building the course is to use the templete course files from the 'Create
DataCamp Course' dialog. This will automatically create a GitHub repository that is linked to DataCamp; any changes that are 
make through DataCamp will update the GitHub repository and visa versa. The GitHub repository will contain three files: 
README.md, course.yml, and chapter1.Rmd.
Readme.md contains helpful information of how to get started, citing resourses to learn more about the process. 
course.yml is a file that contains general information about the course you're creating: title, university, description, 
difficulty level, ect.  
chapter1.Rmd is a template chapter file with examples of 'normal' interative coding exercises and multiple choice questions.
To add more chapters to an R course, create new files in the repository and name them chapter1.Rmd, chapter2.Rmd, chapter3.Rmd
ect.

>>>>

With this increased use of R in classrooms, there is a need for a more effective way to get students familiar with R. While R
software provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate this transition,
popular interactive teaching technologies have been created including Swirl (need to cite this?), LearnR and TryR. These tools 
allow students to work through coding problems while recieving immediate feedback in and out of the classroom. Swirl is an 
open source R software package that allows students to learn R programing in their R console. This interactive learning tool contains several pre-existing lessons but what makes Swirl so popular is its versitality; educators can create their own 
lesson (or tailor a pre-existing one) to fit their curriculum and assign it to students \citep{Carchedi2014}.

@@

DataCamp is also a web application that offers interactive R programing courses but unlike TryR, educators can 
create their own courses that coincide with the lessons or assign a pre-existing DataCamp course. The DataCamp website offers 
free community courses and specialized 'Premium' classes that you need to purchase. However, when used for academic purposes
the premium DataCamp content if free.. (i'll come back to this).

Each chapter in a DataCamp course is made up of modular exercises. Modulariy is critical component in designing a statistical learning tool because it allows independent pieces to be easily added, modified or removed from the entire functionality \citep{Hare2017}. Course exercises can be added, modified, or deleted as new topics arise and instructors can tailor
these exercises to meet the needs of a particular class. The only disadvantage of the modularity feature is that the sessions
are not cummulative; every exercise begins with a clear workspace so any object defined in a previous exercise needs to be 
defined again.

\section{How to Use DataCamp}

\subsection{Pre-existing R courses}
DataCamp has a range of available free community courses that educators can utilize for supplimental R practice.

\subsection{Creating a DataCamp Course}
To create a course on DataCamp you will first need to create a DataCamp account by visiting website\www.datacamp.com/teach and
have a GitHub account. The simplest way to begin building the course is to use the templete course files from the 'Create
DataCamp Course' dialog. This will automatically create a GitHub repository that is linked to DataCamp; any changes that are 
make through DataCamp will update the GitHub repository and visa versa. The GitHub repository will contain three files: 
README.md, course.yml, and chapter1.Rmd.
Readme.md contains helpful information of how to get started, citing resourses to learn more about the process. 
course.yml is a file that contains general information about the course you're creating: title, university, description, 
difficulty level, ect.  
chapter1.Rmd is a template chapter file with examples of 'normal' interative coding exercises and multiple choice questions.
To add more chapters to an R course, create new files in the repository and name them chapter1.Rmd, chapter2.Rmd, chapter3.Rmd
ect.
